Untitled

### 2021-09-16 src/article_figures.Rmd
Run with updated parameters.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("economic_effect_functions.R")
library(knitr)
library(tidyverse)
save_figs = FALSE
save_tables = FALSE
fig_path="~/FRCBS/results-for-eba-paper/pdf"
table_path="~/FRCBS/results-for-eba-paper/table"
all_results_filename <- sprintf("%s/raw-data-2021-06-11.tsv", table_path)
compute=FALSE
```

@@

```{r}
if (compute) {
  all_results <- process_all_data(all_ids)
  write_tsv(all_results, file=all_results_filename)
} else {
  all_results <- read_tsv(file=all_results_filename)  
}
```

@@

```{r}
if (save_tables) {
  library(openxlsx)
  temp <- all_results %>% pivot_wider(names_from=c(variable, type))
  filename <- sprintf("%s/pretty-data-2021-06-11.xlsx", table_path)
  openxlsx::write.xlsx(temp, file = filename, overwrite=TRUE)
}
```

```{r Cost surface}
g <- draw_surface(results=all_results %>% filter(Id == "progesa-both-rf"))
if (save_figs) {
  filename <- sprintf("%s/cme_cost_surface_werr.pdf", fig_path)
  ggsave(filename=filename,  width = 180,  height = 120, units="mm", dpi=600, scale=1.0, device=cairo_pdf)
}
g
```

```{r Probability thresholds}
threshold_range <- seq(0.02, 0.98, 0.02)
data_frames <- map(all_ids, get_data_frame)
#get_thresholds <- function(df,  p=parameters, thresholds = seq(0.1, .9, .1), id=id)
thresholds <- map2_dfr(data_frames, all_ids, function(df, id) get_thresholds(df, parameters, threshold_range, id))

@@

  # Get variable importances from the RF object
  rrfFit_roc <- load_single("~/FRCBS/interval_prediction/results/rrfFit_roc.rdata")
  varimp <- get_rf_df(rrfFit_roc, descript, combined_variables)
  var_imp <- varimp %>%
    mutate(Pretty=fct_rev(Pretty),
           mean=Importance,
           low=ifelse(is.na(Importance), NA, 0),
           high=Importance)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("economic_effect_functions.R")
library(knitr)
library(tidyverse)
save_figs = FALSE
save_tables = FALSE
fig_path="~/FRCBS/results-for-eba-paper/pdf"
table_path="~/FRCBS/results-for-eba-paper/table"
all_results_filename <- sprintf("%s/raw-data-2021-09-03.tsv", table_path)
compute=FALSE

new_fixed_parameters <- list(Pm=2.287, Pd=20.342, F=1, Fn=0.1066, rloss=0.167)
new_parameters <- c(data_parameters, new_fixed_parameters)
```

@@

```{r}
if (compute) {
  all_results <- process_all_data(all_ids)
  write_tsv(all_results, file=all_results_filename)
} else {
  all_results <- read_tsv(file=all_results_filename)  
}
```
The results with RF model:

```{r}
all_results %>% filter(Id=="progesa-both-rf", type=="value", variable %in% c("E6", "a6", "q6"))
```

## Combine the sex specific models

What is the average interval extension, economic effect, and fraction of deferrals avoided, if
we use both male and female models?

```{r}
tmp <- all_results %>% 
  filter(str_detect(Id, "lmm"), type=="value", variable %in% c("E6", "a6", "q6")) %>% 
  separate(Id, sep="-", into=c("data", "sex", "model"), remove=FALSE) %>% 
  pivot_wider(names_from = variable, values_from = value)

tmp %>% group_by(data, model) %>%
  summarise(a6 = sum(a6) - 1,
            E6 = sum(E6),
            q6 = sum(q6)
            )
```

@@

```{r}
if (save_tables) {
  library(openxlsx)
  temp <- all_results %>% pivot_wider(names_from=c(variable, type))
  filename <- sprintf("%s/pretty-data-2021-09-03.xlsx", table_path)
  openxlsx::write.xlsx(temp, file = filename, overwrite=TRUE)
}
```

```{r Cost surface}
g <- draw_surface(results=all_results %>% filter(Id == "progesa-both-rf"), cost_function=do.call(cost_func_factory, new_parameters[c("Pm", "Pd", "F", "Fn", "rloss", "d")]))
if (save_figs) {
  filename <- sprintf("%s/cme_cost_surface_werr.pdf", fig_path)
  ggsave(filename=filename,  width = 180,  height = 120, units="mm", dpi=600, scale=1.0, device=cairo_pdf)
}
g
```

```{r Probability thresholds}
threshold_range <- seq(0.02, 0.98, 0.02)
data_frames <- map(all_ids, get_data_frame)
#get_thresholds <- function(df,  p=parameters, thresholds = seq(0.1, .9, .1), id=id)
thresholds <- map2_dfr(data_frames, all_ids, function(df, id) get_thresholds(df, new_parameters, threshold_range, id))

@@

  # Get variable importances from the RF object
  rrfFit_roc <- load_single("~/FRCBS/interval_prediction/oversampling_results/rrfFit_roc.rdata")
  #rrfFit_roc <- load_single("~/FRCBS/interval_prediction/results/rrfFit_roc.rdata")
  varimp <- get_rf_df(rrfFit_roc, descript, combined_variables)
  var_imp <- varimp %>%
    mutate(Pretty=fct_rev(Pretty),
           mean=Importance,
           low=ifelse(is.na(Importance), NA, 0),
           high=Importance)

### 2021-09-16 src/dummy_classifier.Rmd
Run with updated parameters.

library(tidyverse)
library(knitr)
source("economic_effect_functions.R")
source('../../Hb_predictor_container/src/validate_stan_fit.R', chdir=T)
```

@@

```{r cars}

@@

  result <- tibble(Deferred = glm.probs, 
                   obs = validate$Hb_deferral)

@@

```{r, eval=FALSE}
df1 <- make_threshold_conversion_data_frame(125, -1) 
df2 <- make_threshold_conversion_data_frame(125, -0.1)
df <- bind_rows(`k=-1`=df1, `k=-0.1`= df2, .id="k")
df %>% ggplot(aes(x=Hb, y=Probability, color=k)) + geom_point() + scale_y_continuous(breaks=seq(0, 1, by=0.1)) + labs(colour="Logistic function parameter") + ggtitle("Female")
```

```{r, eval=FALSE}
df1 <- make_threshold_conversion_data_frame(135, -1) 
df2 <- make_threshold_conversion_data_frame(135, -0.1)
df <- bind_rows(`k=-1`=df1, `k=-0.1`= df2, .id="k")
df %>% ggplot(aes(x=Hb, y=Probability, color=k)) + geom_point() + scale_y_continuous(breaks=seq(0, 1, by=0.1)) + labs(colour="Logistic function parameter") + ggtitle("Male")
```

@@

```{r}
use_logistic_regression=TRUE
if (use_logistic_regression) {
  res_female <- dummy_predictor2(train_female, test_female)
  prediction_female <- res_female$result
  fit_female <- res_female$fit

@@

```{r}
#dummy_result <- suppressMessages(process_all_data(dummy2_ids, replicates=100))
dummy_result <- suppressMessages(process_all_data(dummy2_ids))
```

```{r}
df <- dummy_result %>% 
  pivot_wider(names_from=c("variable", "type"), values_from=value, names_glue="{variable} {type}")
names(df) <- str_remove(names(df), " value$")
df <- df %>%
  select("Id", "F1", "F1 low", "F1 high", "threshold6", "threshold12", "E6", "E6 low", "E6 high", "E12", "E12 low", "E12 high")

@@

```{r}
roc_male <- roc_wrapper(prediction_male)
pr_male <- pr_wrapper(prediction_male)
```
```{r}
roc_female
pr_female$pr_plot
roc_male
pr_male$pr_plot
```

>>>>

library(tidyverse)
library(knitr)
source('../../Hb_predictor_container/src/validate_stan_fit.R', chdir=T)
source("economic_effect_functions.R")
```

@@

```{r Logistic regression functions}

@@

  result <- tibble(score = glm.probs, 
                   original_label = validate$Hb_deferral)

@@

```{r Old logistic function plot to convert between Hb threshold and probability for females, eval=FALSE}
df1 <- make_threshold_conversion_data_frame(125, -1) 
df2 <- make_threshold_conversion_data_frame(125, -0.1)
df <- bind_rows(`k=-1`=df1, `k=-0.1`= df2, .id="k")
df %>% ggplot(aes(x=Hb, y=Probability, color=k)) + geom_point() + scale_y_continuous(breaks=seq(0, 1, by=0.1)) + labs(colour="Logistic function parameter") + ggtitle("Female")
```

```{r  Old logistic function plot to convert between Hb threshold and probability for males, eval=FALSE}
df1 <- make_threshold_conversion_data_frame(135, -1) 
df2 <- make_threshold_conversion_data_frame(135, -0.1)
df <- bind_rows(`k=-1`=df1, `k=-0.1`= df2, .id="k")
df %>% ggplot(aes(x=Hb, y=Probability, color=k)) + geom_point() + scale_y_continuous(breaks=seq(0, 1, by=0.1)) + labs(colour="Logistic function parameter") + ggtitle("Male")
```

@@

```{r Fit logistic regression}
use_logistic_regression=TRUE
if (use_logistic_regression) {
  res_female <- dummy_predictor2(train_female, test_female)
  prediction_female <- res_female$result
  fit_female <- res_female$fit

@@

```{r Compute performance measures}
#dummy_result <- suppressMessages(process_all_data(dummy2_ids, replicates=100))
dummy_result <- suppressMessages(process_all_data(dummy_ids))
```

```{r Show the result table}
df <- dummy_result %>% 
  pivot_wider(names_from=c("variable", "type"), values_from=value, names_glue="{variable} {type}")
names(df) <- str_remove(names(df), " value$")
df <- df %>%
  select("Id", "F1", "F1 low", "F1 high", "threshold6", "threshold12", "E6", "E6 low", "E6 high", "E12", "E12 low", "E12 high")

@@

```{r}
roc_male <- roc_wrapper(prediction_male)
pr_male <- pr_wrapper(prediction_male)
```

```{r}
roc_female
pr_female$pr_plot
roc_male
pr_male$pr_plot
```

### 2021-09-16 src/new_economic_parameters.Rmd
Run with updated parameters.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("economic_effect_functions.R")
source("article_figures_functions.R")
library(knitr)
library(tidyverse)
save_figs = TRUE
save_tables = FALSE
dir <- "~/FRCBS/interval-sims/src/new_cost_parameters"
fig_path <- dir
table_path <- dir
all_results_filename <- sprintf("%s/raw-data-2021-08-24.tsv", dir)
compute=FALSE
```

@@

```{r}
new_fixed_parameters <- list(Pm=2.287, Pd=18.08, F=1, Fn=0.1066, rloss=0)

@@

```{r Cost surface}
g <- draw_surface(results=all_results %>% filter(Id == "progesa-both-rf"), cost_function=do.call(cost_func_factory, new_parameters[c("Pm", "Pd", "F", "Fn", "rloss", "d")]))
if (save_figs) {
  filename <- sprintf("%s/cme_cost_surface_werr.pdf", fig_path)
  ggsave(filename=filename,  width = 180,  height = 120, units="mm", dpi=600, scale=1.0, device=cairo_pdf)
}
g
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("economic_effect_functions.R")
source("article_figures_functions.R")
library(knitr)
library(tidyverse)
save_figs = FALSE
#save_tables = FALSE
dir <- "~/FRCBS/interval-sims/src/new_cost_parameters"
fig_path <- dir
table_path <- dir
all_results_filename <- sprintf("%s/raw-data-2021-09-03.tsv", dir)
compute=FALSE
```

@@

```{r}
new_fixed_parameters <- list(Pm=2.287, Pd=20.342, F=1, Fn=0.1066, rloss=0.167)
#new_fixed_parameters <- list(Pm=2.287, Pd=19.96, F=1, Fn=0.1066, rloss=0.167)
#new_fixed_parameters <- list(Pm=2.287, Pd=18.08, F=1, Fn=0.1066, rloss=0)

@@

```{r Cost surface}
cost_function <- do.call(cost_func_factory, new_parameters[c("Pm", "Pd", "F", "Fn", "rloss", "d")])
g <- draw_surface(results=all_results %>% filter(Id == "progesa-both-rf"), cost_function=cost_function)
if (save_figs) {
  filename <- sprintf("%s/cme_cost_surface_werr.pdf", fig_path)
  ggsave(filename=filename,  width = 180,  height = 120, units="mm", dpi=600, scale=1.0, device=cairo_pdf)
}
g
```
